Hydras \& Co.

### 2022-07-02 doc/hydras.tex
add author address

\author{Pierre Castéran\\ Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800, \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

>>>>

% \author{Pierre Castéran\\ Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France\footnote{ email: pierre casteran at gmail dot com} \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
% Russel O'Connor\cite{OConnor05}.}}
% \date{\today}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}
